{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-10 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
        \;\\
        Initialize any $\gamma_0 >= 0$, $(x_0, v_0)$ or equivalently $(x_0, y_0), (y_0, v_0)$. 
        Given any sequence $(\rho_k)_{k\ge0}, (\alpha_k)_{k \ge0}$ such that for all integer $k\ge 0$, $\textcolor{red}{\rho_k \ge 0}$, $\alpha_k \in (0, 1)$. 
        The algorithm generates a sequence of $(x_k, y_k, v_k)$ such that they satisfy for all $k\ge 0$ recursively: 
        \begin{align*}
            \gamma_k &:= \left.\begin{cases}
                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 1,
                \\
                \gamma_0 & k = 0. 
            \end{cases}\right\rbrace,
            \\
            \hat \gamma_{k + 1} &:= L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
            \\
            y_k &= 
            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= 
            \hat\gamma^{-1}_{k + 1}
            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{align*}
    \end{definition}
    \begin{observation}
        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018}. 
    \end{observation}

@@

            F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2

@@

    \begin{proposition}[R-WAPG fits into Momentum Form]\label{prop:wapg-momentum-form}
        \;\\
        Suppose any sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ satisfies recursively the conditions
        $L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$ where $\rho_{k} \in \ge 0\; \forall k \ge0$. 
        Assume that $0 \le \mu < L$. 
        If $\alpha_k$ is used in the similar triangle form to generate the iterates $(x_k, y_k, v_k)$. 
        Then the iterates are algebraically equivalent to: 
        \begin{align*}
            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
            \\
            y_{k + 1} &= 
            x_{k + 1} + 
            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
        \end{align*}
        In the special case when $\mu = 0$, the momentum term admits simpler representation 
        \begin{align*}
        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
        & = \alpha_{k + 1}(\alpha_k^{-1} - 1). 
        \end{align*}
    \end{proposition}
    \begin{proof}

@@

            L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_k \mu. 

>>>>

    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
        \;\\
        Initialize any $\gamma_0 \ge 0$, $(x_0, v_0)$ or equivalently $(x_0, y_0), (y_0, v_0)$. 
        Given any sequence $(\rho_k)_{k\ge0}, (\alpha_k)_{k \ge0}$ such that for all integer $k\ge 0$, $\textcolor{red}{\rho_k \ge 0}$, $\alpha_k \in (0, 1)$. 
        The algorithm generates a sequence of $(x_k, y_k, v_k)$ such that they satisfy for all $k\ge 0$ recursively: 
        \begin{align*}
            \gamma_k &:= \left.\begin{cases}
                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 1,
                \\
                \gamma_0 & k = 0. 
            \end{cases}\right\rbrace,
            \\
            \hat \gamma_{k + 1} &:= L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
            \\
            y_k &= 
            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= 
            \hat\gamma^{-1}_{k + 1}
            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{align*}
    \end{definition}
    \begin{observation}
        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018}. 
    \end{observation}

@@

            & F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2

@@

    \begin{proposition}[R-WAPG fits into Momentum Form]\label{prop:wapg-momentum-form}
        \;\\
        Suppose any sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ satisfies recursively the conditions
        $L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$ where $\rho_{k} \ge 0\; \forall k \ge0$. 
        Assume that $0 \le \mu < L$. 
        If $\alpha_k$ is used in the similar triangle form to generate the iterates $(x_k, y_k, v_k)$. 
        Then the iterates are algebraically equivalent to: 
        \begin{align*}
            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
            \\
            y_{k + 1} &= 
            x_{k + 1} + 
            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
        \end{align*}
        In the special case when $\mu = 0$, the momentum term admits simpler representation 
        \begin{align*}
        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
        & = \alpha_{k + 1}(\alpha_k^{-1} - 1). 
        \end{align*}
    \end{proposition}
    \begin{proof}

@@

            L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_{k + 1} \mu. 
